03 Data Vizualization

### 2022-11-04 03_data_viz.Rmd
added inset plot to figure 2

## (PASSING) Memory effect on gen_d

@@

## (PASSING) dF plot
Using memory-corrected values

@@

## (PASSING) Turnover plot

@@

## Abundance versus turnover

@@

turnover_fit_tidy <- broom::tidy(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))

p_abundance_v_turnover2 <- turnover %>% 
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d_mc
  )) +
  # Individual data points
  geom_point(
    aes(color = terrain),
    alpha = 0.6,
    ) +
  geom_polygon(
    data = hull_data,
    aes(
       fill = terrain,
       color = terrain
       ),
     show.legend = FALSE,
     alpha = 0.15,
     size = 0.15
    ) +
  geom_smooth(
    method = "lm",
    formula = "y~x",
    se = FALSE,
    color = "gray",
    size = 0.3,
    linetype = "dotted"
  ) +
  scale_color_manual(values = terrain_color_swatch) +
  theme_bw() +
  labs(
    x = "µg analyte (per g soil)",
    y = TeX("Turnover rate (day$^{-1}$)"),
    size = TeX("$ \\Delta ^2H$ (ppm)"),
    color = " "
  ) +
  theme(
    strip.background = element_blank(),
    legend.position = c(0.9, 0.87),
    panel.grid = element_blank(),
  )
p_abundance_v_turnover2

@@

## (PASSING) Literature Rates of Cell Turnover by Method

@@

## (PASSING) BacDive FA profiles

@@

## (FAILING) Compare extraction efficiency

@@

## (PASSING) Example chromatogram
```{r}
# plot an example chromatogram

@@

## (PASSING) Turnover distributions

@@

## (PASSING) Detection limit

@@

## (PASSING) Fatty Acid Abundances

@@

## (PASSING) Visible colony

@@

## (PASSING) Assimilation efficiency histogram

>>>>

## Memory effect on gen_d

@@

## F1A: dF plot
Using memory-corrected values

@@

## F1B: Turnover plot

@@

## F2: Abundance versus turnover

@@

turnover_fit_tidy <- broom::tidy(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
writexl::write_xlsx(turnover_fit_tidy, path = "data_output/turnover_fit_lm.xlsx")
writexl::write_xlsx(turnover_fit_glance, path = "data_output/turnover_fit_lm_stats.xlsx")

p_abundance_v_turnover2 <- turnover %>% 
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d_mc
  )) +
  # Individual data points
  geom_point(
    aes(color = terrain),
    alpha = 0.6,
    ) +
  geom_polygon(
    data = hull_data,
    aes(
       fill = terrain,
       color = terrain
       ),
     show.legend = FALSE,
     alpha = 0.15,
     size = 0.15
    ) +
  geom_smooth(
    method = "lm",
    formula = "y~x",
    se = FALSE,
    color = "gray",
    size = 0.3,
    linetype = "dotted"
  ) +
  scale_color_manual(values = terrain_color_swatch) +
  theme_bw() +
  labs(
    x = "µg analyte (per g soil)",
    y = TeX("Compound-specific growth rate (day$^{-1}$)"),
    size = TeX("$ \\Delta ^2H$ (ppm)"),
    color = " "
  ) +
  theme(
    strip.background = element_blank(),
    legend.position = c(0.9, 0.55),
    legend.background = element_blank(),
    panel.grid = element_blank(),
  )
p_abundance_v_turnover2

@@

### Inset Plot

```{r}
p_abundance_v_turnover_inset <- turnover %>% 
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d_mc
  )) +
  # Individual data points
  geom_point(
    aes(color = terrain),
    alpha = 0.6,
    size = 2
    ) +
  coord_cartesian(xlim = c(0, 5), ylim = c(0, 0.01)) +
  scale_color_manual(values = terrain_color_swatch) +
  theme_bw() +
  labs() +
  theme(
    strip.background = element_blank(),
    legend.position = "NA",
    legend.background = element_blank(),
    panel.grid = element_blank(),
    axis.title = element_blank(),
    panel.background = element_blank()
  )
p_abundance_v_turnover_inset
```

### Draft 2 with inset plot!

```{r}
p_abundance_v_turnover_w_inset <- ggdraw(p_abundance_v_turnover2) +
  draw_plot(
    p_abundance_v_turnover_inset, 
    x = 0.63, 
    y = 0.63, 
    width = 0.35, 
    height = 0.35
    )
cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
                   plot = p_abundance_v_turnover_w_inset,
                   base_height = 6,
                   base_width = 8)
```

## F3: Literature Rates of Cell Turnover by Method

@@

## SF: BacDive FA profiles

@@

## Compare extraction efficiency

@@

## Example chromatogram
```{r}
# plot an example chromatogram

@@

## Turnover distributions

@@

## SF: Detection limit

@@

## SF: Fatty Acid Abundances

@@

## SF: Visible colony

@@

## SF: Assimilation efficiency histogram
